{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation

### 2012-02-01 paper/paper.tex
corrected sentence
extended motivation

The idea Barthe, Rezk, Russo and Sabelfeld phrased in \cite{Barthe07} was to close
this leak (formally called \textit{covert channel}) by annotating the byte-code
of the program\footnote{Most mobile devices use some sort of byte-code e.g. Android.} with security
labels according to the confidentiality of the information, which causes the scheduler to hide
threads that leak information from the attacker.

@@

\begin{definition}
The junction points are computed by a function $jun: \mathcal{P} \rightarrow \mathcal{P}$. This function is defined
on all junction points $[c]^n$ in the source program and its domain is $jun(n) = max \{i\ |\ i \in tregion(n)\} + 1$.
\end{definition}

>>>>

The idea Barthe, Rezk, Russo and Sabelfeld phrased in \cite{Barthe07} was to close
this leak (formally called \textit{covert channel}) by annotating the byte-code
of the program\footnote{Most mobile devices use some sort of byte-code e.g. Android.} with security
labels according to the confidentiality of the information, which causes the scheduler to hide
threads that leak information from the attacker. Their formal model allows to
formulate this idea as a framework, which can be instantiated with many programming languages,
schedulers and types of byte-code.

@@

\begin{definition}
The junction points are computed by a function $jun: \mathcal{P} \rightarrow \mathcal{P}$. This function is defined
on all junction points $[c]^n$ in the source program as $jun(n) = max \{i\ |\ i \in tregion(n)\} + 1$.
\end{definition}
